\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
simplified derivation of parameter estimator
another text problem example

Alg.~\ref{programGenerativeModel} is a procedure for drawing
samples from $\probability[p|\mathcal{D},\theta]$.  In practice, we
enumerate programs rather than sampling them.  Enumeration proceeds by
a depth-first search over the random choices made by
Alg.~\ref{programGenerativeModel}; we wrap the depth-first search
in iterative deepening to build $\lambda$-calculus
expressions in order of their probability.

@@

\subsection{Sleep-G: Inducing the DSL}\label{grammarInductionSection}

@@

Alg.~\ref{mainAlgorithm} describes how we combine program search,
recognition model training, and DSL induction.
We note the following implementation details:
(1) We perform a wake cycle before each of the sleep cycles.
(2) On the first iteration, we do \emph{not} train the recognition model on samples from
the generative model because a DSL has not yet been learned --
we instead train the network to only maximize $\mathcal{L}_{\text{AE}}$.
%% (3) Because the frontiers can grow very large,
%% we only keep around the top $10^4$ programs $p$ in each frontier $\mathcal{F}_x$
%% with the highest likelihood $\probability[x,p|\mathcal{D},\theta]$.
(3) During both DSL induction and neural net training, we calculate Eq.~\ref{AIC} and $\mathcal{L}_{\text{RM}}$
by only summing over the top $K$
programs in $\mathcal{F}_x$ as measured by $\probability[x,p|\mathcal{D},\theta]$ -- we found that $K = 2$ sufficed.
(4) For added robustness, we enumerate programs from both the generative model and the recognition model.

@@

     \STATE $\mathcal{D},\theta\gets $induceDSL$(\{\mathcal{F}^{\theta}_x\cup\mathcal{F}^{q}_x\}_{x\in X})$   \footnotesize{\textbf{(Sleep-G)}}
     %% \STATE Define $Q_x(z) \propto \begin{cases}
     %%   \probability[x|z]\probability[z|\mathcal{D}_i,\theta_i]&x\in \mathcal{F}_x\\
     %%   0&x\not \in \mathcal{F}_x
     %% \end{cases}
      \ENDFOR
 \STATE \textbf{return} $\mathcal{D},\theta,q$
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}
  \centering\begin{tabular}{ll}\toprule
    Input&Output\\\midrule
cqbHT$>$aIKd$<$szW& 	AIKD\\
YBW$>$TIg$<$WSho 	&TIG\\
%DkI$>$DwKI$<$xaPoc& 	DWKI\\
KfvTh$>$Dbl$<$OIJso 	&DBL
    \\\bottomrule
  \end{tabular}

  \vspace{0.25cm}

  \begin{minipage}{\linewidth}
    \centering
    $f($\code{s}$) \,=\, $\code{(}$f_3$\code{ (split '>' (upper s)) '<')}
  \end{minipage}
  \caption{A string edit task and the program \system writes for it. $f_3$ is a discovered DSL subroutine, defined in Tbl.~\ref{textPrimitives}.}\label{exampleTextProblem}
\end{figure}

>>>>

Alg.~\ref{programGenerativeModel} is a procedure for drawing
samples from the generative model $(\mathcal{D},\theta)$.  In practice, we
enumerate programs rather than sampling them.  Enumeration proceeds by
a depth-first search over the random choices made by
Alg.~\ref{programGenerativeModel}; we wrap the depth-first search
in iterative deepening to build $\lambda$-calculus
expressions in order of their probability.

@@

\subsection{Sleep-G: Learning a DSL (Generative Model)}\label{grammarInductionSection}

@@

Alg.~\ref{mainAlgorithm} describes how we combine program search,
recognition model training, and DSL induction.
We note the following implementation details:
(1) We perform a wake cycle before each of the sleep cycles.
(2) On the first iteration, we do \emph{not} train the recognition model on samples from
the generative model because a generative model has not yet been learned --
we instead train the network to only maximize $\mathcal{L}_{\text{AE}}$.
%% (3) Because the frontiers can grow very large,
%% we only keep around the top $10^4$ programs $p$ in each frontier $\mathcal{F}_x$
%% with the highest likelihood $\probability[x,p|\mathcal{D},\theta]$.
(3) During both DSL induction and neural net training, we calculate Eq.~\ref{AIC} and $\mathcal{L}_{\text{RM}}$
by only summing over the top $K$
programs in $\mathcal{F}_x$ as measured by $\probability[x,p|\mathcal{D},\theta]$ -- we found that $K = 2$ sufficed.
(4) For added robustness, we enumerate programs from both the generative model and the recognition model.

@@

     \STATE $\mathcal{D},\theta\gets $induceDSL$(\{\mathcal{F}^{\theta}_x\cup\mathcal{F}^{q}_x\}_{x\in X})$  \hspace{1.1cm} \footnotesize{\textbf{(Sleep-G)}}
     %% \STATE Define $Q_x(z) \propto \begin{cases}
     %%   \probability[x|z]\probability[z|\mathcal{D}_i,\theta_i]&x\in \mathcal{F}_x\\
     %%   0&x\not \in \mathcal{F}_x
     %% \end{cases}
      \ENDFOR
 \STATE \textbf{return} $\mathcal{D},\theta,q$
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}
  \centering\begin{tabular}{ll|ll}\toprule
    Input&Output&Input&Output\\\midrule
cqbHT$>$aIKd$<$W& 	AIKD&BgZQ..PBBnD & BgZQ. \\
YBW$>$TIg$<$WS 	&TIG& qqfgg..mNIx & qqfgg. 
%DkI$>$DwKI$<$xaPoc& 	DWKI\\
%KfvTh$>$Dbl$<$OIJso 	&DBL
\\\midrule
\multicolumn{2}{l|}{$f(\text{\code{s}}) = $\code{(}$f_3$\code{ (split '>' } }&
\multicolumn{2}{l}{$f(\text{\code{s}}) = $\code{(}$f_1$\code{ s '.' 0)}}
\\
\multicolumn{2}{l|}{\hspace{1.1cm}\code{(upper s)) '<')}}
\\\bottomrule
  \end{tabular}

  %% \vspace{0.25cm}

  %% \begin{minipage}{\linewidth}
  %%   \centering
  %%   $f($\code{s}$) \,=\, $
  %% \end{minipage}

  \caption{Two string edit tasks (top) and the programs \system writes for them (bottom). $f_3$ are $f_1$  discovered DSL subroutines, defined in Tbl.~\ref{textPrimitives}.}\label{exampleTextProblem}
\end{figure}
